The AGN fuelling/feedback cycle in nearby radio galaxies - VI. Visible light IFU observations and results

### 2020-11-16 paper.tex
Final changes (in this round)
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   paper_noComments.tex
	modified:   refs.bib

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[IFS Study of Low-power Radio Galaxies]{An Integral-field
  Spectroscopic Study of Low-power Radio Galaxies}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert. JW: not deliberate - I'd left this to ask you about who to include.}}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

@@

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
Clarify.)} stellar spectrum} \added{fits to the stellar 
spectrum for all bins}. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}

@@

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs \added{\citep[e.g.][]{Worthey1992}}{\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
\removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
$0.1$~kpc)}`added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) \added{with very high metallicity projecting southwards from below the eastern}
\removed{along the south-east} branch of the molecular gas (\removed{white} 
\added{cyan} contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

\removed{As can be seen from the maps in Appendix~\ref{sec:maps}, 
both NGC~612 and NGC~3100 have significant off-centred ionised 
gas emission.} {\bf (What do you mean by ``significant'' here? Bright?
  Clarify. Equivalently, why is the off-centred emission in IC~1459
  and NGC~1316 not considered significant?)} 
\added{The ionised gas emission for both NGC~612 ).} In NGC~612, 
the ionised gas does not appear related to either the radio jet 
(extending $\approx200$~kpc to the East and West of the galaxy 
centre) or the CO, but in NGC~3100 the ionised gas is spatially 
coincident with both the radio jet and the gap in the CO ring.

@@

The radial profiles shown in Figs.~\ref{fig:Ha_profile_MUSE} and
\ref{fig:Hb_profile_VIMOS} suggest that all the galaxies with
spatially-extended Balmer emission in our Southern Sample have a
central point source as the dominant source of the ionising
photons. The H$\beta$ profile of NGC~612 has a larger scatter,
suggesting that stellar processes also have some impact (likely
radiation from pAGB stars {\bf (Again.)}, as NGC~612 has a low
star-formation rate). {\bf (Check what the SFR of NGC~612 actually is,
  to confirm your suspicion, e.g.\ from non-nuclear radio continuum or
  MIR/FIR emission. This may already be discussed in Ilaria's
  papers.)}

@@

The mass\,--\,excitation (MEx) plot of \citet{Juneau2011} is useful to
classify galaxies with intermediate excitation levels
($0.5<\mathrm{[\ion{O}{iii}]/H\beta}<8.0$), particularly as it does
not depend on faint lines such as the [\ion{N}{i}] doublet. We use
here the calibrations by \citet{Nyland2016}, including an attempt to
separate LINERs powered by AGN from those powered by pAGB stars (i.e.\
LIERs, with [\ion{O}{iii}] equivalent widths $>0.8$~\AA). We again
focus on the nuclear regions, using a central circular aperture of
radius $3\arcsec$ for all our Southern Sample galaxies. The resulting
diagnostic plot is shown in Fig.~\ref{fig:MEx}.

@@

In terms of absorption line strengths and stellar populations
(Sections~\ref{sec:absorption} and \ref{sec:stellarPop}), we found for
our Southern Sample galaxies a gradient of the central Mg~$b$ line
strength versus stellar velocity dispersion relation remarkably
similar to that of \citet{Ziegler1997}. Most of the galaxies in our
Southern Sample have typical ETG properties, with old, metal-rich
stellar populations. {\bf (What about $\alpha$-elements? You should
  also summarise those results here.)} The few exceptions are NGC~612
and NGC~1316, that are both significantly younger than most ETGs, and
NGC~3557, that has a young core. All $3$ KDCs contain old stellar
populations, and they are consistent with being merger remnants. The
KDCs found in Section~\ref{sec:StarKine} are also in agreement with
the KDC age\,--\,size relation found by \added{\citet{McDermid2006}} 
\removed{\citet{Kuntschner2010}} in optically-selected ETGs (see 
Section~\ref{subsec:popKDC}). {\bf (See my previous comment about 
McDermid et al.\ 2006, and perhaps quote it here instead or 
additionally.)}

If cold (e.g.\ molecular) gas is accreted on to the central black
holes of our Southern Sample galaxies to power their nuclear
activities, then unless it is accreted in a highly turbulent fashion
some of it should form stars within the accretion discs
\citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}. If this
is indeed the case, and these young stellar populations are bright
enough to dominate the light, then they should stand out in the
central few spaxels. However, detection of such populations could
prove difficult due to contamination from the AGN continua, the
presence of dust (see Table~\ref{tab:sample} for a description of the
dust morphologies of our Southern Sample galaxies) and the rapid rate
at which a young stellar population fades. In fact, our best-fitting
age maps show no evidence of an abnormally young central stellar
population in any of our galaxies. This is consistent with the results
of other authors such as \citet{GonzalezDelgado2004} and
\citet{Sarzi2005b} with \textit{Hubble Space Telescope} (\textit{HST})
spectra and \citet{CidFernandes2004} with ground-based spectra. In
addition, in Section~\ref{subsec:Diagnostics}, we showed that there is
no evidence of an extended ionising source consistent with ongoing
star formation in any of our targets. {\bf (It seems to me that this
  paragraph is missing a short ``conclusion''. Add one... no evidence
  of any ongoing SF in any of our galaxies?)}

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and \removed{possibly} \added{occasionally} exceed {\bf (Again, why ``possibly''? They either always
  exceed, generally exceed, occasionally exceed, or never exceed!
  Check and clarify.)}, the typical masses observed in ETGs,

@@

All galaxies with detected emission lines in our Southern Sample show
line ratios characteristic of LINER or Seyfert~2 galaxies. In
particular, we classify $9$ of our $11$ galaxies as LINERs, and we can
conclusively attribute the ionising photons to the central AGN in $5$
of those. The only Seyfert~2 is the fast rotator IC~1531. This is
consistent with the results of \citet{Nyland2016}, who showed that all
Atlas$^\text{3D}$ ETGs classified as Seyferts are also fast rotators.
The final galaxy, PKS~718-34, has no emission line detection (i.e.\ it
is classified as passive). {\bf (These statistics do not match those
  in paragraph 2 of Sub-section~8.1, where only $9$ galaxies are said
  to be detected in ionised gas (rather than $10$ as inferred
  here). The culprit seems to be NGC~1399, which is listed as
  non-detected in Sub-section~8.1 and Appendix~A, has no emission line
  map in Appendix~B, but is nevertheless classified as a LINER in
  Table~4... how is this possible?! Check and fix/harmonise here, in
  Sub-section~8.1, in Table~4, and in the second paragraph of
  Appendix~A.)}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[IFS Study of Low-power Radio Galaxies]{The AGN fuelling/feedback cycle in 
nearby radio galaxies - VI. Visible light IFU observations and results}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert.}\\ {\bf JW: not deliberate - I'd left this to ask you about who to include.
    On the title are we up to paper IV? Just checking I haven't missed one!}\\ {\bf Also any ideas for a better title?}}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2020}

@@

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
Clarify.)} stellar spectrum} \added{fits to the stellar 
spectrum for all bins}. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range 
of the NGC~1316 spectra was restricted to $<5800$~\AA. \added{The best-fitting 
stellar spectra were then extrapolated above 5800~\AA.}

@@

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs \added{\citep[e.g.][]{Worthey1992}}{\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
\removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
$0.1$~kpc)}\added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) \added{with very high metallicity projecting southwards from below the eastern}
\removed{along the south-east} branch of the molecular gas (\removed{white} 
\added{cyan} contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

As can be seen from the maps in Appendix~\ref{sec:maps}, 
both NGC~612 and NGC~3100 have \removed{significant off-centred ionised 
gas emission.} \added{ionised gas emission offset from the center of the 
galaxy.} {\bf (What do you mean by ``significant'' here? Bright?
  Clarify. Equivalently, why is the off-centred emission in IC~1459
  and NGC~1316 not considered significant?)} In NGC~612, 
the ionised gas does not appear related to either the radio jet 
(extending $\approx200$~kpc to the East and West of the galaxy 
centre) or the CO, but in NGC~3100 the ionised gas is spatially 
coincident with both the radio jet and the gap in the CO ring.

@@

The radial profiles shown in Figs.~\ref{fig:Ha_profile_MUSE} and
\ref{fig:Hb_profile_VIMOS} suggest that all the galaxies with
spatially-extended Balmer emission in our Southern Sample have a
central point source as the dominant source of the ionising
photons. The H$\beta$ profile of NGC~612 has a larger scatter,
suggesting that stellar processes also have some impact. \added{Indeed 
\citet{Asabere2016} found NGC~612 to have a star formation rate an 
order of magnitude high than that of NGC~1316.} \removed{(likely
radiation from pAGB stars {\bf (Again.)}, as NGC~612 has a low
star-formation rate).} {\bf (Check what the SFR of NGC~612 actually is,
  to confirm your suspicion, e.g.\ from non-nuclear radio continuum or
  MIR/FIR emission. This may already be discussed in Ilaria's
  papers.)}

@@

The mass\,--\,excitation (MEx) plot of \citet{Juneau2011} is useful to
classify galaxies with intermediate excitation levels
($0.5<\mathrm{[\ion{O}{iii}]/H\beta}<8.0$), particularly as it does
not depend on faint lines such as the [\ion{N}{i}] doublet. We use
here the calibrations by \citet{Nyland2016}, including an attempt to
separate LINERs powered by AGN from those powered by pAGB stars (i.e.\
LIERs, with [\ion{O}{iii}] equivalent widths $>0.8$~\AA). We again
focus on the nuclear regions, using a central circular aperture of
radius $3\arcsec$ for all our Southern Sample galaxies. The resulting
diagnostic plot is shown in Fig.~\ref{fig:MEx}. \added{In particular, this 
method allows us to classify NGC~1399 as a LINER (see 
Table~\ref{tab:derivedProp}).}

@@

In terms of absorption line strengths and stellar populations
(Sections~\ref{sec:absorption} and \ref{sec:stellarPop}), we found for
our Southern Sample galaxies a gradient of the central Mg~$b$ line
strength versus stellar velocity dispersion relation remarkably
similar to that of \citet{Ziegler1997}. Most of the galaxies in our
Southern Sample have typical ETG properties, with old, metal-rich\added{, alpha-enhanced}
stellar populations. {\bf (What about $\alpha$-elements? You should
  also summarise those results here.)} The few exceptions are NGC~612
and NGC~1316, that are both significantly younger than most ETGs, and
NGC~3557, that has a young core. All $3$ KDCs contain old stellar
populations, and they are consistent with being merger remnants. The
KDCs found in Section~\ref{sec:StarKine} are also in agreement with
the KDC age\,--\,size relation found by \added{\citet{McDermid2006}} 
\removed{\citet{Kuntschner2010}} in optically-selected ETGs (see 
Section~\ref{subsec:popKDC}). {\bf (See my previous comment about 
McDermid et al.\ 2006, and perhaps quote it here instead or 
additionally.)}

If cold (e.g.\ molecular) gas is accreted on to the central black
holes of our Southern Sample galaxies to power their nuclear
activities, then unless it is accreted in a highly turbulent fashion
some of it should form stars within the accretion discs
\citep[e.g.][]{Collin1999, Diamond-Stanic2012, LaMassa2013}. If this
is indeed the case, and these young stellar populations are bright
enough to dominate the light, then they should stand out in the
central few spaxels. However, detection of such populations could
prove difficult due to contamination from the AGN continua, the
presence of dust (see Table~\ref{tab:sample} for a description of the
dust morphologies of our Southern Sample galaxies) and the rapid rate
at which a young stellar population fades. In fact, our best-fitting
age maps show no evidence of an abnormally young central stellar
population in any of our galaxies. This is consistent with the results
of other authors such as \citet{GonzalezDelgado2004} and
\citet{Sarzi2005b} with \textit{Hubble Space Telescope} (\textit{HST})
spectra and \citet{CidFernandes2004} with ground-based spectra. In
addition, in Section~\ref{subsec:Diagnostics}, we showed that there is
no evidence of an extended ionising source consistent with ongoing
star formation in any of our targets. {\bf (It seems to me that this
paragraph is missing a short ``conclusion''. Add one... no evidence
of any ongoing SF in any of our galaxies?)} \added{We conclude, therefore,
that the accretion is either turbulent or any star-formation is weak
and consequently will not have a significant effect on the overall galactic
evolution processes.}

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and \removed{possibly} \added{occasionally} exceed {\bf (Again, why ``possibly''? They either always
  exceed, generally exceed, occasionally exceed, or never exceed!
  Check and clarify.)}, the typical masses observed in ETGs.

@@

All galaxies with detected emission lines in our Southern Sample show
line ratios characteristic of LINER or Seyfert~2 galaxies. In
particular, we classify $9$ of our $11$ galaxies as LINERs, and we can
conclusively attribute the ionising photons to the central AGN in $5$
of those. The only Seyfert~2 is the fast rotator IC~1531. This is
consistent with the results of \citet{Nyland2016}, who showed that all
Atlas$^\text{3D}$ ETGs classified as Seyferts are also fast rotators.
The final galaxy, PKS~718-34, has no emission line detection (i.e.\ it
is classified as passive). {\bf (These statistics do not match those
  in paragraph 2 of Sub-section~8.1, where only $9$ galaxies are said
  to be detected in ionised gas (rather than $10$ as inferred
  here). The culprit seems to be NGC~1399, which is listed as
  non-detected in Sub-section~8.1 and Appendix~A, has no emission line
  map in Appendix~B, but is nevertheless classified as a LINER in
  Table~4... how is this possible?! Check and fix/harmonise here, in
  Sub-section~8.1, in Table~4, and in the second paragraph of
  Appendix~A.). JW: NGC~1399 is classified using the MEx plot in 
  Section~8.3.2. I've added a sentence in that section to make that
  explicit.}

### 2020-11-16 paper_noComments.tex
Final changes (in this round)
 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   paper_noComments.tex
	modified:   refs.bib

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[IFS Study of Low-power Radio Galaxies]{An Integral-field
  Spectroscopic Study of Low-power Radio Galaxies}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Ilaria Ruffa,$^{4}$ Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ Rosita Paladino,$^{4}$ Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and Timothy Davis$^{5}$
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK

@@

In reality, the field of view does not always fully contain 
a given fitted ellipse. When this 
is the case, we follow the method of \citet{Emsellem2007}, where 
$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
where $A_\text{s}$ is the area contained within 
the field of view of the given ellipse. {\it For a given galaxy, we fit ellipses 
as described above, up to $R_\text{m}=R_\text{max}$, where 
$R_\text{max}$ is defined such that  
$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.
} The value $\epsilon_\text{e}$, the ellipticity of this largest 
fitted ellipse, is given in Column~3 of 
Table~\ref{tab:classify}.

@@

Using a central circular aperture with a radius of $2\arcsec$ in each
datacube, we measure $\sigma_0$ and Mg~$b$ at a degraded spectral
resolution of $8.4$~\AA\ full-width at half-maximum (FWHM), chosen
such that the transformation functions of \citet{Vazdekis2010} can be
used to change literature measurements from the Lick/IDS system to the
LIS. The results are shown in Fig.~\ref{fig:globalMg}, with the
best-fitting linear relationship
% (found using \textsc{lts\_linefit} from \citealt{Cappellari2013})
indicated by the solid black line, with a gradient of
$3.3\pm1.0$~\AA~dex$^{-1}$. We noted that NGC~1316 is again ana possible
outlier. Excluding NGC~1316 from the fit
yields a gradient of $2.5\pm0.7$~\AA~dex$^{-1}$ (green dashed line in
Fig.~\ref{fig:globalMg}). Both fits are in very good agreement with
the gradient found by \citet{Ziegler1997} for a sample of elliptical
galaxies in the Virgo and Coma clusters of galaxies
% using data from \citet{Dressler1987}
($2.7$~\AA~dex$^{-1}$, transformed to the LIS system using the
functions of \citealt{Vazdekis2010}; blue dotted line in
Fig.~\ref{fig:globalMg}).

@@

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and occasionally exceed, the typical masses observed in ETGs,

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[IFS Study of Low-power Radio Galaxies]{The AGN fuelling/feedback cycle in 
nearby radio galaxies - VI. Visible light IFU observations and results}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Ilaria Ruffa,$^{4}$ Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ Rosita Paladino,$^{4}$ Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and Timothy Davis$^{5}$
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  $^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}

@@

In reality, the field of view does not always fully contain 
a given fitted ellipse. When this 
is the case, we follow the method of \citet{Emsellem2007}, where 
$R_\text{m}$ is redefined as $R_\text{m}\equiv\sqrt{A_\text{s}/\pi}$, 
where $A_\text{s}$ is the area contained within 
the field of view of the given ellipse. For a given galaxy, we fit ellipses 
as described above, up to $R_\text{m}=R_\text{max}$, where 
$R_\text{max}$ is defined such that  
$\frac{A_\text{s}(R_\text{max})}{A_\text{ellipse}(R_\text{max})} 
\equiv 0.15$ or $R_\text{max} = R_\text{e}$, which ever is smallest.
The value $\epsilon_\text{e}$, the ellipticity of this largest 
fitted ellipse, is given in Column~3 of 
Table~\ref{tab:classify}.

@@

Using a central circular aperture with a radius of $2\arcsec$ in each
datacube, we measure $\sigma_0$ and Mg~$b$ at a degraded spectral
resolution of $8.4$~\AA\ full-width at half-maximum (FWHM), chosen
such that the transformation functions of \citet{Vazdekis2010} can be
used to change literature measurements from the Lick/IDS system to the
LIS. The results are shown in Fig.~\ref{fig:globalMg}, with the
best-fitting linear relationship
% (found using \textsc{lts\_linefit} from \citealt{Cappellari2013})
indicated by the solid black line, with a gradient of
$3.3\pm1.0$~\AA~dex$^{-1}$. We noted that NGC~1316 is again an
outlier. Excluding NGC~1316 from the fit
yields a gradient of $2.5\pm0.7$~\AA~dex$^{-1}$ (green dashed line in
Fig.~\ref{fig:globalMg}). Both fits are in very good agreement with
the gradient found by \citet{Ziegler1997} for a sample of elliptical
galaxies in the Virgo and Coma clusters of galaxies
% using data from \citet{Dressler1987}
($2.7$~\AA~dex$^{-1}$, transformed to the LIS system using the
functions of \citealt{Vazdekis2010}; blue dotted line in
Fig.~\ref{fig:globalMg}).

@@

In Section~\ref{sec:gas}, we showed that our Southern Sample galaxies
have ionised gas masses of $10^4$\,--\,$10^6$~$\mathrm{M_\odot}$. As
our sample contains particularly massive galaxies, high ionised gas
masses are not unexpected, but these masses are at the upper limit of,
and occasionally exceed, the typical masses observed in ETGs.
